Fourmile Calibrations and Output

### 2025-02-25 params.Rmd
minor

# Compute y_text just above the boxplot whiskers
combo <- combo %>%
  group_by(param, burn, input_data) %>%
  mutate(y_text = max(value, na.rm = TRUE) * 1.08) %>%  # Slightly above max value
  ungroup()

>>>>

# text above boxplots
combo <- combo %>%
  group_by(param, burn, input_data) %>%
  mutate(y_text = max(value, na.rm = TRUE) * 1.08) %>%  # Slightly above max value
  ungroup()
